### 2020-02-14 UbiCompSubmission/bp_studyMethod.tex
update with gail's changes

In the second month of the study, we also offered participants two one-hour Tai Chi classes per week (each in the middle of the day) and asked them to attend one class a week. We chose to offer Tai Chi class for two reasons: first, to incentivise participants for their continued participation and for keeping them engaged; and second, for their said benefits of reducing stress based on our consultation with researchers in psychiatry, psychology and more specifically on mindfulness practices.

>>>>

Keeping participants engaged in an eight-week study can be
difficult. In the second month of the study, largely to incent participants to
continue, we offered participants two one-hour Tai Chi classes per
week (each in the middle of the day) and asked them to attend one
class a week. The choice of Tai Chi provided a link to mindfulness,
a topic of growing interest in communities. Consultations we held
with researchers in psychiatry and psychology suggested Tai Chi as
a good link to mindfulness and an intervention that might alleviate
stress. By recording attendence of participants at the Tai Chi
sessions, we are able to analyze the impact of the sessions
on the results. As a brief summary, the impact of the
sessions was minimal; a a result, we present an analysis
of the effects in the Discussion section of the paper.
